---
title: "MSDS Second Case Study"
author: "Alec Lepe, Che Cobb"
date: "11/28/2018"
output: 
  html_document:
    fig_width: 6
    fig_height: 4
  keep_md: true
---
### Load Libraries
```{r setup, include=FALSE, echo=FALSE}
#install.packages("data.table")
#install.packages("readxl")
#install.packages("ggplot2")
#install.packages("reshape")
library("data.table")
library("readxl")
library("tidyverse")
library("ggplot2")
library("reshape")
knitr::opts_chunk$set(fig.width = 10, fig.length=10, fig.asp = 1/3,  message=TRUE,echo=FALSE,cache=TRUE)
fig.path = "~/MSDS-6306-Second-Case-Study/Figures"
```
### Reproducibility: Session Info
```{r aeessionInfo}
sessionInfo()
```
### Load Data
```{r LoadData}
casedata=data.table::as.data.table(readxl::read_excel("~/2nd-Case-Study/Data/CaseStudy2-data.xlsx"))
#save(casedata,file="~/MSDS-6306-Second-Case-Study/Data/CaseStudy2-data.RData")
#load("~/MSDS-6306-Second-Case-Study/Data/CaseStudy2-data.RData")
dim(casedata)
str(casedata)
```
### Detect and Delete Non-Relevant Data
``` {r DeleteData}
cns=c()
for (cn in colnames(casedata)){
  if(length(table(casedata[[cn]]))==1){
    print(cn)
    cns=append(cn,cns)
  }
}
for (cn in cns){
  print(paste(cn,names(table(casedata[[cn]])),table(casedata[[cn]])))
  casedata=casedata[,!cn,with=F]
}
```
Deleted: *Standard Hours*, *Over18*, and *EmplyoeeCount* where there is only one value.
``` {r AttritionCount}
barplot(table(casedata[["Attrition"]]), main="Attrition Count",col=c("Green","Red"))
table(casedata[["Attrition"]])/nrow(casedata)
```
### How does age relate to attrition?
``` {r AttritionCountByAge,echo=T}
ID="Age"
yes=casedata[,sum(Attrition=="Yes"),ID]; colnames(yes)[2]="Yes"
no=casedata[,sum(Attrition=="No"),ID];   colnames(no)[2]="No"
temp=merge(yes,no,all=T)
temp=melt(temp,id=ID)
temp=as.data.frame(temp)
colnames(temp)=c(ID,"Attrition","Count")
temp %>% ggplot(aes(fill=Attrition,y=Count,x=eval(as.symbol(ID))))+geom_bar(stat="identity")+xlab(ID)
```
Here we can see that attrition is greatest between 29 and 35.
``` {r AttritionProportionByAge}
temp=merge(temp,as.data.table(temp)[,sum(Count),ID])
colnames(temp)[ncol(temp)]="Total"
temp[["Proportion"]]=temp[["Count"]]/temp[["Total"]]
ggplot(temp,aes(fill=Attrition,y=Proportion,x=eval(as.symbol(ID))))+geom_bar(stat="identity")+xlab(ID)+ggtitle(paste(ID,"vs Attrition"))
```
Here we see that attrition is greater at earlier ages, with a noticeable peak at age 58.
``` {r age58}
temp[temp[["Age"]]==58,]
```
### How does business travel relate to attrition?
``` {r AttritionCountByBusinessTravel}
ID="BusinessTravel"
yes=casedata[,sum(Attrition=="Yes"),ID]; colnames(yes)[2]="Yes"
no=casedata[,sum(Attrition=="No"),ID];   colnames(no)[2]="No"
temp=merge(yes,no,all=T)
temp=melt(temp,id=ID)
temp=as.data.frame(temp)
colnames(temp)=c(ID,"Attrition","Count")
temp=merge(temp,as.data.table(temp)[,sum(Count),ID])
colnames(temp)[ncol(temp)]="Total"
temp[["Proportion"]]=temp[["Count"]]/temp[["Total"]]
ggplot(temp,aes(fill=Attrition,y=Proportion,x=eval(as.symbol(ID))))+geom_bar(stat="identity")+xlab(ID)+ggtitle(paste(ID,"vs Attrition"))
```

